Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-24 manuscript/manuscript.Rmd
added a bit of discussion on methods

\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{figures/DecisionApproaches.pdf}
  \caption{
  \label{fig:decision approaches}
  TBD.
  }
\end{figure}

@@

# Results

We trained a DRL agent to obtain a candidate policy
\begin{align*}
  \pi: (X_t,Y_t,Z_t) \mapsto h_t
\end{align*}
for eq. \eqref{eq:3d model}.
The agent could fully and precisely observe the state of the system at each time step and decide on its harvest based on this information. 
The agent was trained using the PPO algorithm, using a neural network with two hidden layers of 64 neurons to express $\pi$.
Details of the training process may be found in App. \ref{app:tbd}.
Our code is available at TBD.

>>>>

@@

# Methods and Results

## Methods

Model-based controls, such as MSY, are known to have serious deficiencies when the model used to find the optimal control does not match reality.
As mentioned, for the particular case of fisheries this can lead to depletion of resources and affect severely the surrounding ecosystems.
Because of this, we have opted to compare the performance of several data-based approaches to fishery control (see Fig. \ref{fig:decision approaches}).

As shown in Fig. \ref{fig:decision approaches}, these data-based strategies rely on choosing a family of *approximating functions* for the policy, $\mathcal{P}:=\{\pi_\theta\}_\theta$, parametrized by some vector $\theta$.
These functions are deterministic policies, i.e. they map states to actions, or, specifically,
$$
  \pi_\theta : \mathbb{R}^n \to \mathbb{R}_+,
$$
where, as before, $n$ is the number of species.
The aim of the optimization process is to find a parameter choice $\theta^*$ for which $\pi_{\theta^*}$ is optimal within $\mathcal{P}$.

Our focus here will be comparing two data-based approaches: *constant mortality* and *DRL*.
Constant mortality is, as the name suggests, based on MSY.

For the constant mortality approach, we choose a linear harvest $\pi_F(N_t)= F X_t$, where the parameter $F$ is scalar, and where $N_t = (X_t,\ \dots\ )\in \mathbb{R}^n$.
This first control is intended to delineate how one might apply MSY to a real-world fishery.
We will also compare a TAC-inspired rule of thumb which uses, instead, the parameter value $F_{\text{TAC}} = 0.8 F^*$.
In App. \ref{app:tbd}, we discuss several other MSY-based approaches which yield similar results to the strategies just discussed.

In the DRL approach, we instead parametrize $\mathcal{P}$ using a neural network with two hidden layers of 64 neurons.
Our hypothesis is that the additional flexibility yielded by neural networks will allow the agent solutions that are better than MSY based approaches.

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/DecisionApproaches.pdf}
  \caption{
  \label{fig:decision approaches}
  TBD.
  }
\end{figure}

## Results

\textbf{Reword a bit.}
We trained a DRL agent to obtain a candidate policy
\begin{align*}
  \pi: (X_t,Y_t,Z_t) \mapsto h_t
\end{align*}
for eq. \eqref{eq:3d model}.
The agent could fully and precisely observe the state of the system at each time step and decide on its harvest based on this information. 
The agent was trained using the PPO algorithm, using a neural network with two hidden layers of 64 neurons to express $\pi$.
Details of the training process may be found in App. \ref{app:tbd}.
Our code is available at TBD.
